Minimal trap-spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-05 cmsb22.tex

\begin{document}
%
\title{Minimal trap-spaces of Logical models are maximal siphons of their Petri net encoding}
\titlerunning{Minimal trap-spaces as maximal siphons}
\author{Van-Giang Trinh\inst{1}\orcidID{0000-0001-6581-998X} \and \\
  Sylvain Soliman\inst{2}\orcidID{0000-0001-5525-7418}}
% \authorrunning{F. Author et al.}

\institute{
  LIS, Aix-Marseille Université, Marseille, France\\
  \email{Trinh.Van-Giang@lis-lab.fr}
  \and
  Lifeware team, Inria Saclay center, Palaiseau, France\\
  \email{Sylvain.Soliman@inria.fr}%\\
  %\url{http://lifeware.inria.fr/~soliman/}
}

>>>>

\begin{document}
%
\title{Minimal trap-spaces of Logical models are maximal siphons of their Petri net encoding}
\titlerunning{Minimal trap-spaces as maximal siphons}
\author{Van-Giang Trinh\inst{1}\orcidID{0000-0001-6581-998X} \and \\
  Sylvain Soliman\inst{2}\orcidID{0000-0001-5525-7418} \and \\
  Kunihiko Hiraishi\inst{3}\orcidID{0000-0003-1750-1891} \and \\ Belaid Benhamou\inst{1}
  }

\authorrunning{Trinh et al.}

\vangiang{I added two other authors. Prof. Belaid Benhamou is currently my postdoctoral supervisor and he will also involve in the topic on siphons. Prof. Kunihiko Hiraishi was my doctoral supervisor. I obtained the method for trap space computation when I was a researcher in his lab and he also contributes to this method. Of course, they will involve in revising the papers. Is this OK for you?}

\institute{
  LIS, Aix-Marseille Université, Marseille, France\\
  \email{\{Trinh.Van-Giang, belaid.benhamou\}@lis-lab.fr}
  \and
  Lifeware team, Inria Saclay center, Palaiseau, France\\
  \email{Sylvain.Soliman@inria.fr}%\\
  %\url{http://lifeware.inria.fr/~soliman/}
  \and
  School of Information Science, Japan Advanced Institute of Science and Technology, Japan\\
  \email{hira@jaist.ac.jp}
}
